Finite Property Convex Elicitation Notes

### 2018-08-07 cvx-fin-notes.tex
typo
a duality result!

% alphabetical order, by convention
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\I}{\mathcal{I}}
\renewcommand{\P}{\mathcal{P}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}
\renewcommand{\P}{\mathcal{P}}

\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}

@@

Note that the definition of $\R'$ is a generalization of its definition as $[\underline r, \overline r]$ in Proposition~\ref{prop:fplc-trim-char}.
\begin{conjecture}
  Let $L:\reals^d \to\reals^\Y$ be FPLC, and $\R$ the vertices of $\sum_{y\in\Y} L(\cdot)_y$.
  Then $\trim(\Gamma_L) \equiv \Gamma_L\cap \R'$ where $\R' = \conv \{ \argmin_{r\in\reals^d} L(r)_y \cap \R : y\in\Y\}$.
\end{conjecture}

@@

>>>>

% alphabetical order, by convention
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\I}{\mathcal{I}}
\renewcommand{\P}{\mathcal{P}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\ones}{\mathbbm{1}}

@@

Note that the definition of $\R'$ is a generalization of its definition as $[\underline r, \overline r]$ in Proposition~\ref{prop:fplc-trim-char}.
\begin{conjecture}
  Let $L:\reals^d \to\reals^\Y$ be FPLC, and $\R$ the vertices of $\sum_{y\in\Y} L(\cdot)_y$.
  Then $\trim(\Gamma_L) \equiv \Gamma_L\cap \R'$ where $\R' = \conv \{ \argmin_{r\in\reals^d} L(r)_y : y\in\Y\} \cap \R$.
\end{conjecture}

@@

\section{Duality}

\begin{theorem}
  Every elicitable property is essentially elicited by a $|\Y|$-dimensional convex loss function (i.e.,\ is $|\Y|$-embeddable).
\end{theorem}
\begin{proof}
  To work exclusively with convex functions, we will consider a score for $\Gamma$ and then a convex loss.
  Let $\Gamma:\Delta(\Y)\toto\R$ be the given elicitable property, with $\R$ arbitrary, elicited by $S:\R\times\Y\to\reals$.
  Let $G : \Delta(\Y) \to \reals$ be the convex expected score function given by $G(p) = \max_{r\in\R} \E_p S(r,Y)$.
  Let $C : \reals^\Y \to \reals \cup \{\infty\}$ be the convex conjugate of $G$, so $C = G^*$.
  By \raf{results with Ian} we know that for some $\D \subseteq \partial G(\Delta(\Y)) \subseteq \reals^\Y$ we have some bijection $\varphi : \R \to \D$ such that $\Gamma(p) = \varphi^{-1}(\D \cap \partial G(p))$.
  \raft{In other words, $\Gamma$ is a relabeling of subgradients of $G$}
  Thus, we can write
  \begin{equation}
    \label{eq:1}
    r \in \Gamma(p) \iff \varphi(r) \in \partial G(p) \iff p \in \partial C(\varphi(r))~,
  \end{equation}
  where the final equivalence follows from convex duality.
  \raft{Of course, we need to be careful here; this only holds if $G$ is proper and lower semi-continuous, but those should both hold for us.}

  Now define $L(\hat r,y) = C(\hat r) - \hat r \cdot \ones_y$ on the report space $\hat \R = \conv(\D)$;
  we will show that $L$ essentially elicits $\Gamma$.
  As $L$ is convex, we may write the optimality condition as
  \begin{equation}
    \label{eq:2}
    \hat r \in \Gamma_L(p) \iff \hat r \in \argmax_{\hat r'} \E_pL(\hat r',Y) \iff 0 \in \partial \E_pL(\hat r,Y)~,
  \end{equation}
  where of course the subgradient $\partial$ is with respect to $\hat r$.
  Plugging in our definition of $L$, we have
  \begin{align*}
    0 \in \partial \E_pL(\hat r,Y)
    & \iff 0 \in \partial \E_p \left(C(\hat r) - \hat r \cdot \ones_Y\right)
    \\
    & \iff 0 \in \partial \left(C(\hat r) - \hat r \cdot p\right)
    \\
    & \iff 0 \in \partial C(\hat r) - \{p\}
    \\
    & \iff p \in \partial C(\hat r)~.
  \end{align*}
  Putting this together with eq.~\eqref{eq:1}, we have for any $\hat r \in \D$ that
  \begin{equation}
    \label{eq:3}
    \hat r \in \Gamma_L(p) \iff p \in \partial C(\hat r) \iff \varphi^{-1}(\hat r) \in \Gamma(p)~,
  \end{equation}
  which implies that $L$ essentially elicits $\Gamma$ for this $\varphi$.
  (The trivially induced map $\varphi:\R\to\hat\R$ is injective as $\varphi:\R\to\D$ was a bijection.)
  \raf{If we assume $\Gamma$ is non-redundant, I believe we also have $\Gamma = \trim(\Gamma_L)$ using $\D$ is the report set.}
\end{proof}

\newpage\newpage
